### 2012-02-15 docs/FAQ/faq.tex
why is maestro "hard"

>>>>

\item {\em Why is \maestro\ so ``hard'' to use (e.g.\ as compared to a
  compressible code)?}

There are several complexities to the algorithm that don't have
straightforward compressible counterparts.  These mainly involve the
role of the base state and the constraint equation.

Care must be taken to setup an initial model/initial base state that
respects the thermodynamics in \maestro\ and is in hydrostatic equilibrium.
Best results are attained when the model is processed with the \maestro\
EOS and reset into HSE, as is done in the {\tt initial\_model} routines.
Because \maestro\ builds off of the base state, any flaws in that initial 
state will influence the subsequent behavior of the algorithm.

The constraint equation brings another complexity not seen in compressible
codes---information is instantly communicated
across the grid.  In compressible codes you can track down a problem by
watching where it starts from and watching it move one cell per dt.  In
\maestro\ things can go wrong in multiple places without it being obvious
where the root problem is.
